---
title: "Alcohol vs Seat choice"
author: "Gianna Chevez"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data


## Now add in boxplot
```{r}
boxplot(alcohol~Seat,data=davisdata)
```

The boxes are not disjoint. In the boxplot, the median of the back box is higher than that of the front and middle boxes. The front and middle boxes exhibit similar sizes, though the middle box contains a greater number of outliers compared to the front box.  
  
  

## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```


The back seat data shows the highest values and most variability, with a median of 3.5 and mean of 8.56. The middle seat data is intermediate with a median of 1 and a mean of 3.33. The front seat data has the smallest values and least variability, with a median of 0 and a mean of 1.79.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The probability of obtaining these results is one out of ten thousand. Further analysis is required to determine which sets differ from one another.
```{r}
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

The analysis indicates that the back seat data differs significantly from both the front and middle seat data. However, the middle seat and front seat data do not show significant difference from each other, but they are distinct  from the back seat data. 

## Conclusions

I created a box plot to visually represent the consumption across different rows, highlighting the difference in consumption levels. The numerical summary revealed that the back row consumed twice as much alcohol compared to the other rows. When comparing three or more groups, a one way ANOVA is used to determine if there are significant differences among them. If the ANOVA test yields a p value between 0 and 1, further investigation is needed, which may involve additional tests to understand the specific differences between the groups. To further explore these differences, I performed additional analyses and plotted a revised model that highlighted the distinct contrast in alcohol consumption in the back. 